Extended Abstract

### 2021-05-04 paper/paper.tex
Start working on intro

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Type inference for the pi calculus with linear and shared channel types.

@@

\hypertarget{types}{%
\subsection{Types}\label{types}}

@@

\hypertarget{type-system}{%
\subsection{Type System}\label{type-system}}

>>>>

\begin{abstract}
  The linear \picalc{} is a well-known substructural type system for the \picalc{}:
  it is a common target for the encoding of session-typed languages \todo{cite},
  and it in direct correspondence with classical linear logic \todo{cite}.

  Type inference for the linear \picalc{} comes with its own challenges:
  for one, processes themselves are untyped, and thus typing constraints only apply to the typing contexts;
  moreover, typing constraints on usage annotations \emph{cannot always be eagerly solved in open processes}.

  We approach the first challenge using \emph{co-contextual type inference} \cite{ErdwegBKKM15}, where processes are traversed bottom-up and constraints are collected (and when possible eagerly solved) and merged on context splits.
  We approach the latter challenge by allowing the resolution of some of the constraints to be deferred.
  We state soundness and completeness theorems that take this deferral of constraint resolution into account.
  We state a progress (?) theorem that shows that only those constraints that need to be deferred are deferred.
  \todo{be more precise}
  We are working on mechanising our work in Agda.
\end{abstract}

\maketitle

\section{Introduction}\label{introduction}

We define an untyped but well scoped \picalc{} using type-level de Bruijn \todo{cite} indices \autoref{syntax}.
We define a small expression language within the process syntax to handle composite sum and product types.
On top of the well-scoped syntax we provide the standard linear type-system using context-splits \autoref{type-system}.
The type system is indexed by a typing context that admits unsolved metavariables.
These unsolved metavariables are however well kinded: either types or usage annotations.

\todo{insert example showing why we need deferral}

We split typing inference into constraint collection and constraint solving \autoref{inference}.
We start by defining constraints on types and usage annotations \autoref{constraints}
We collect constraints bottom-up, creating extra \emph{merging} constraints on context splits.
This allows type-inference to be easily parallelisable.
We postulate soundness and completeness theorems that allow for constraint solving to be deferred \autoref{inference-theorems}.

@@

\section{Type System}\label{type-system}

\subsection{Types}\label{types}

@@
